Designing Types for R, Empirically

### 2020-10-14 paper/main.tex
minor

In this section, we set out to propose a candidate design for a type
language to describe the arguments and return values of R functions.
The goal is not to propose a final design, but rather to propose a
starting point for an iterative design process.  Fig.~\ref{types}
presents our type language. An early design choice was to stay close
to the R language and only depart in small and hopefully
non-controversial ways.  Functions types have the form \FUN{A_1,
  \dots, A_n}\T where each $\A_i$ argument is either a type \T or
\VARGS, a variable length argument list. The rest of this section
details and motivates our design.

>>>>

In this section, we set out to propose a candidate design for a type
language to describe the arguments and return values of R functions.
The goal is not to propose a final design, but rather a
starting point for an iterative design process.

Fig.~\ref{types} presents our type language. An early design choice
was to stay close to the R language and only depart in small and
hopefully non-controversial ways.  Functions types have the form
\FUN{A_1, \dots, A_n}\T where each $\A_i$ argument is either a type \T
or \VARGS, a variable length argument list. The rest of this section
details and motivates our design.
